\section{Music, Art, Physical Education, and Health Program}

\textbf{Music \& Arts} \\
IDS offers MUSIC \& ARTS subjects from grade 7 to grade 10. Music and Arts deal with all possible music and arts skills that a learner may comprehend. It will allow the students to explore their creative minds in arts and understand critical concepts in music. The subject aims to cultivate a student's sense of awareness of his/her own strength and appreciation of their possible output outside the classroom. Music \& Arts will also discuss how to play musical instruments, analyze musical terms and how to use their body, space and time in performing arts. The subject will teach them musical skills where they can explore Broadway productions and performing etiquette in productions. Moreover, it teaches the students to have confidence in themselves and be a more holistic individual in their daily lives. 

\textbf{Physical Education} \\
Physical Education is a course that is offered to MSU-IIT IDS students from Grade 7 to Grade 12. It encompasses different areas such as physical fitness, dance, individual/dual sports, combative sports, and team sports. It enables the students to develop a deeper understanding and appreciation of the different topics in fitness, dance, and sports while acquiring the necessary skills and competencies towards the attainment of a healthy and active lifestyle. 

This subject deals with the different components of health and skill related fitness and their applications in dance, sports, and recreational activities. It provides the learners with knowledge of training principles and kinds of exercises to develop a personalized fitness plan which is a tool towards physical fitness. It also seeks to instill deeper appreciation of the role of physical activities to the attainment of the total well-being of an individual. 

\textbf{Health} \\
IDS offers Health subjects at every grade level to ensure that all its graduates can make healthy decisions in life. Thus, Health subjects offer health and wellness, disease prevention, and health skills to develop healthy habits, refrain from risky behaviors, and opt for healthy choices.


\subsection{Program Outcomes}
Upon completing the subject, students will be able to: 

\subsubsection{\textbf{Music and Arts}}

\begin{itemize}[label=PO\arabic*.]
	\item [PO1.] To provide students with basic knowledge in the fundamentals of music \& arts that they can use and possibly apply in their career and social interactions.
	\item [PO2.] To instill the students with proper information and skills in performing arts and stage presence as well how they can carry themselves in front of a large crowd. 
	\item [PO3.] To train and develop students holistically discovering their different strengths not only in academics but also in music \& arts where they can enhance and apply in their daily activity.
	\item [PO4.] To provide a sense of belongingness and culture appreciation in learning Asian music \& history that cultivates not only arts but also culture.
\end{itemize}

\subsubsection{\textbf{Physical Education}}

\begin{itemize}[label=PO\arabic*.]
	\item  [PO1.] Acquire knowledge and skills in the various areas of physical education such as fitness, dance, individual/dual sports, team sports, and recreation. 
	\item  [PO2.] Deeply understand the importance of fitness, dance, sports, and recreation in the pursuit of health and wellness.
	\item  [PO3.] Utilize the knowledge about exercises and training principles in the formulation and implementation of fitness plans toward a healthy lifestyle and leading to a healthy population and a progressive community.
\end{itemize}

\subsubsection{\textbf{Health}}

\begin{itemize}[label=PO\arabic*.]
	\item  [PO1.] develop health habits. 
	\item  [PO2.] abstain from risky behaviors.
\end{itemize}


\subsection{Outcome Mapping} 

\subsubsection{\textbf{Music \& Arts}}
The abovementioned MUSIC \& ARTS program outcomes map themselves to the overall IDS outcomes in the following manner: 

\begin{center}
	\begin{tabular}{ l | c | c | c | c}
		IDS Outcomes				& PO1		 	& PO2		  &  PO3	     &  PO4 \\
		1. Academically Prepared	& \checkmark	& \checkmark  &  		     &      \\
		2. Holistically Developed	& \checkmark 	&			  &	 \checkmark  &  	\\
		3. Patriotic 				& 				&   		  &				 &  \checkmark \\
		4. Collaborative			& 				&			  &	\checkmark	 &  \checkmark \\
		5. Adaptable				&				& \checkmark  &	\checkmark	 &  \checkmark \\
	\end{tabular}
\end{center}

PO1 is mapped to school outcomes A \& B as the nature of learning the basic knowledge of music \& arts and holistic learning molds students to be equipped with the fundamentals of music and arts.

PO2 is mapped to A \& C as the nature of being adaptable and academically well rounded in skill subjects helps the students.

PO3 is mapped to B, D \& E as the nature of training students with music \& performing arts skills helps them experience a holistic education, collaborative learning and engagements with other subjects as well as being adaptable.

PO4 is mapped in C, D \& E as the nature of instilling and cultivating Filipino roots and culture in arts and performing arts strengthens their patriotism and allows them to be collaborative in exploring and adaptive in widening Asian music \& arts.

\subsubsection{\textbf{Physical Education}}
The abovementioned Physical Education (PE) program outcomes map themselves to the overall IDS outcomes in the following manner: 

\begin{center}
	\begin{tabular}{ l | c | c | c }
		IDS Outcomes				& PO1		 	& PO2		  &  PO3	      \\
		1. Academically Prepared	& \checkmark	& 			  &  		      \\
		2. Holistically Developed	& 			 	& \checkmark  &	 \checkmark   \\
		3. Patriotic 				& 				&   		  &				  \\
		4. Collaborative			& 				&			  &	\checkmark	  \\
		5. Adaptable				&				& 			  &	\checkmark	  \\
	\end{tabular}
\end{center}

PO1 is mapped to School Outcome A, as the knowledge and skills that the students acquire in the subject prepare them for more complex learning in the tertiary level of education. PO2 is mapped to Outcome B, as the different learning areas in physical education enable the students to be more mature in the physical, mental, emotional, and social aspects. Lastly, PO3 is mapped to Outcomes B, D, and E, since the learning in physical education provides a positive impact to the individual and community and contributes to nation building. 

\subsubsection{\textbf{Health}}
The abovementioned Health program outcomes map themselves to the overall IDS outcomes in the following manner: 

\begin{center}
	\begin{tabular}{ l | c | c  }
		IDS Outcomes				& PO1		 	& PO2		  	 \\
		1. Academically Prepared	& \checkmark	& \checkmark			  	 \\
		2. Holistically Developed	&  \checkmark   & \checkmark     \\
		3. Patriotic 				& \checkmark    & \checkmark 		    \\
		4. Collaborative			& \checkmark	& \checkmark		    \\
		5. Adaptable				& \checkmark	& \checkmark		     \\
	\end{tabular}
\end{center}

PO1 and PO2 are mapped to school outcomes A, B, D, and E. First, opting for healthy choices in life will benefit the students holistically. Consequently, this includes academic and non-academic aspects. Finally, opting for healthy choices will foster collaboration and adaptability as students work together and be flexible when they participate in group health-related activities as an application to the health lessons, of which some are geared for Filipino youth.

\subsection{Subject Descriptions}

\subsubsection{\textbf{Music \& Arts}}
The Grade 7 To Grade 10 music \& arts subject which is briefly described below, which is taken over the entire school year. 

\begin{subject}
	MUSIC \& ARTS 7: Fundamentals of Music \& Arts 
	\hfill
	(2hrs/week)
\end{subject}
FUNDAMENTALS OF MUSIC 1: \\
This topic dwells about music appreciation and the basic fundamentals that students need to know. Fundamentals of music will anchor in how to read and follow musical symbols as well as learning the different musical instruments with its different parts, this is in relation to their grade 8
for instrument playing and performing.

ARTS: VISUAL ARTS \\
This topic will focus on enhancing the student’s artistic skills. Different medium of arts will be introduced to the students and teaching them to be patient and imaginative in their works.

\begin{subject}
	MUSIC \& ARTS 8: Fundamentals of music \& Performing art (Recital) 
	\hfill
	(2hrs/week)
\end{subject}

FUNDAMENTALS OF MUSIC 2: \\
This topic is a continuation of Fundamentals of Music 1. Topics will be more in depth and more in application and analysis. Students will be taught to dissect and analyze note reading and music comprehension.

PERFORMING ARTS: RECITAL \\
Lessons and meetings in this topic will all be about performing arts. Performing arts in this grade level will focus on basic stage presence and stage \& audience ethics in performing. Students will apply the learning musical instruments \& compositions and combine it with performing. The output will also be action research in collaboration with the other subjects.


\begin{subject}
	MUSIC \& ARTS 9: Music History \& Performing arts (Broadway) 
	\hfill
	(2hrs/week)
\end{subject}

MUSIC HISTORY: \\
Topics in this year level will aim to introduce famous music figures from the past. Music history explores past music and the historical connection of each era. To better understand the music development and progress of music, music history will teach students more in music perception especially to the current music that they listen.


PERFORMING ARTS: BROADWAY \\
During this year level, students will be taught how to apply performing arts from grade 8 to musical Broadway. In a much broader and bigger audience, performing arts will tackle more in stage movements, stage presence, body expression and artistic creativity in stage management and props creation.

\begin{subject}
	MUSIC \& ARTS 10: Asian Music \& Performing arts (Production)
	\hfill
	(2hrs/week)
\end{subject}

ASIAN MUSIC: \\
The topics in this year level will be composed of Asian music information. Students will listen to each country’s distinct music, explore the sound of the instruments, and understand each country’s culture and practices. Asian music will take students to learning the music of Asia and application of their previous understanding of music from Western in comparison to Asia.

PERFORMING ARTS: ASIAN MUSIC PRODUCTION \\
Performing arts in this year's level will be more on students' own creative minds and concepts. In comparison to the previous performing arts from grade 7 to grade 9 where they base everything from a source, students on this level will learn to create their own concept and creative production. Each production will still be in line with the Asian countries as discussed in the 2nd quarter. Students will learn more about concept and idea building to help them think more critically and precision in their decisions.

\subsubsection{\textbf{Physical Education}}
The Physical Education subject is offered in all grade levels. Briefly included here are the different topics and their descriptions. 

\begin{subject}
	Physical Fitness 
	\hfill
	(1hr/week)
\end{subject}
PE 1 is offered in Grade 7 and is the backbone of all PE subjects in the higher grade levels. This subject deals with the deeper understanding of the different physical fitness components and their roles towards the attainment of fitness and well-being. Such knowledge, along with the knowledge in training principles, is required to be able to formulate fitness plans or blueprints towards a healthy lifestyle. 

\begin{subject}
	Dance 
	\hfill
	(1hr/week)
\end{subject}
PE 2 deals with the different kinds and categories of dance, both in the Filipino and western cultures. In this subject, students will be able to develop dancing skills, identify traditional dances of different regions, categorize social dances, and recognize the importance of dance to overall wellbeing. 

\begin{subject}
	Choice of Individual/Dual Sport and Combative Sport
	\hfill
	(1hr/week)
\end{subject}
PE 3 is the introduction to sports, specifically the individual and dual sports, and combative sports. Along with the basic knowledge and skills of the chosen sports, the subject also allows students’ development of acceptable personal and social behavior that demonstrate respect for themselves and their peers, set personal goals, manage stress, build self-confidence and develop mental toughness, while maintaining physical fitness.

\begin{subject}
	Team Sports
	\hfill
	(1hr/week)
\end{subject}
PE 4 deals with the development of basic skills in various team sports to promote cooperation and sportsmanship, and lifelong recreational habits in the pursuit of optimal health, wellness and healthy lifestyle. Furthermore, it develops in the students an appreciation of the concepts of fair play, honest competition, good sportsmanship attitude, and teamwork. It also promotes leadership skills and fosters qualities of cooperation, tolerance, consideration, trust, and confidence. Furthermore, the subject trains potential students in sports officiating and management. 

\subsubsection{\textbf{Health}}

\begin{subject}
	Health 7: Health and Wellness I 
	\hfill
	(2hrs/week)
\end{subject}
Health 7 covers the fundamentals of Health. It is a holistic approach that encompasses physical, mental, and social aspects of health, with an emphasis on physical health. It addresses the key concepts of health in achieving and maintaining wellness for a quality life.


\begin{subject}
	Health 8: Health and Wellness II
	\hfill
	(2hrs/week)
\end{subject}
Health 8 covers the fundamentals of Health. It is a holistic approach that encompasses physical, mental, and social aspects of health, with an emphasis on injury prevention, environmental health and drug education. It addresses the key concepts of health in achieving and maintaining wellness for a quality life.


\begin{subject}
	Health 9: Disease Prevention I
	\hfill
	(2hrs/week)
\end{subject}
Health 9 covers the fundamentals of Health. It is a holistic approach that encompasses physical, mental, and social aspects of health, with an emphasis on communicable disease prevention and mental health. It addresses the key concepts of health in achieving and maintaining wellness for a quality life.

\begin{subject}
	Health 10: Disease Prevention II
	\hfill
	(2hrs/week)
\end{subject}
Health 10 covers the fundamentals of Health. It is a holistic approach that encompasses physical, mental, and social aspects of health, with an emphasis on non-communicable disease prevention and selected health topics. It addresses the key concepts of health in achieving and maintaining wellness for a quality life.
