\section{Mathematics Program}
Mathematics is included in the curriculum of IDS Junior and Senior High School to provide students with fundamental skills crucial for their personal and academic development. These subjects nurture logical reasoning, problem-solving capabilities, and numerical fluency, which are invaluable across various domains such as science, technology, finance, and everyday decision-making. Additionally, the mathematics subjects offered in IDS plays a vital role in fostering critical thinking and analytical skills, contributing to intellectual growth and cognitive enhancement. Early exposure to mathematical concepts aims to empower students with confidence and proficiency, equipping them to tackle future academic endeavors and navigate the challenges of an increasingly quantitative society.

\subsection{Program Outcomes}
Program outcomes in mathematics refer to the overarching goals and skills that students are expected to achieve upon completion of a mathematics program. These outcomes provide a comprehensive view of the knowledge, abilities, and competencies that students should have acquired during their mathematical education. Here are the program outcomes for mathematics: 
\begin{enumerate}[label=\Alph*.]
	\item{Mathematical proficiency to prepare for future studies:}
	\begin{itemize}
		\item Apply advanced mathematical concepts to develop innovative solutions.
		\item Build a solid foundation in algebra, geometry, and other core areas to succeed in higher-level mathematics courses.
		\item Develop skills that are valuable for success in college and future careers.
	\end{itemize}
	\item{Creative and critical thinking}
	\begin{itemize}
		\item Demonstrate divergent thinking skills in answering open-ended tasks. 
		\item Evaluate mathematical arguments and proofs for validity and logical coherence.
		\item Synthesize information from various sources to approach challenging mathematical problems.
		\item Develop critical thinking skills by analyzing and solving mathematical problems using different strategies.
	\end{itemize}
	\item{Mathematical Communication}
	\begin{itemize}
		\item Effectively communicate mathematical ideas through written reports, presentations, and discussions.
		\item Justify mathematical solutions through clear and coherent explanations.
		\item Present mathematical findings and arguments to peers and teachers.
	\end{itemize}
	\item{Real-World Applications}
	\begin{itemize}
		\item Apply mathematical concepts to solve real-world issues in a variety of fields, including engineering, science, and finance.
		\item Recognize the value of mathematics in the professional and academic environments
	\end{itemize}
\end{enumerate}

\subsection{Outcome Mapping}
The above mentioned Math program outcomes map themselves to the overall IDS Outcomes in the following manner:
\begin{center}
	\begin{tabular}{ l | c | c | c | c }
		IDS Outcomes				& Outcome A 	& Outcome B   &  Outcome C & Outcome D 	\\
		1. Academically Prepared	& \checkmark	& 		 	  &  		   & \checkmark\\
		2. Holistically Developed	& 				&			  &	 			& \\
		3. Patriotic 				& 				&			  &				&	\\
		4. Collaborative			& 				&			  &	\checkmark	& \\
		5. Adaptable				&				& \checkmark  &				&	\\
	\end{tabular}
\end{center}



\subsection{Subject Descriptions}
Every year level has one Math subject, each of which is briefly described here. For the full syllabus of each subject, please refer to Appendix A: Subject Syllabi.

\begin{subject}
	Math 7: Elementary Algebra
	\hfill
	(5hrs/week)
\end{subject}
This course is designed to provide an introductory overview of the fundamental concepts of algebra. The primary focus is on developing a solid understanding of key concepts related to sets, real numbers, algebraic expressions, polynomials, linear equations, and linear inequalities. The goal is to prepare students for Mathematics 8 by establishing a strong foundation in these core algebraic principles. This program offers students a comprehensive mathematical framework that is essential for awide range of academic fields and practical decision-making.

\begin{subject} Math 8: Intermediate Algebra
	\hfill
	(3 hrs/week)
\end{subject}
This course emphasizes on the understanding of basic concepts of Linear Equations, Systems of Linear Equations and Inequalities, Quadratic Equation and Inequalities , Cartesian Coordinate System, Rational Expressions, Equations and Applications as preparation for Math 9.

\begin{subject} Math 8.1 Geometry
	\hfill
	(3hrs/week)
\end{subject}
This course deals with the measurement, properties and relationships of points, lines, angles, and planes.It provides students with the opportunity to develop mathematical reasoning. Reasoning mathematically means developing and testing conjectures through Deduction. Algebra skills will also be integrated throughout each chapter and reinforced within the Geometry exercises.

\begin{subject} Math 9: Advanced Algebra
	\hfill
	(4hrs/week)
\end{subject}
This course is offered to Grade 9 students at the Integrated Developmental School, MSU-IIT. The course includes topics solving rational exponents, radicals, variations, sequences and series, functions and relations, different kinds of functions and their graphs, inverse functions, polynomial functions, and their applications to the real world. It also contains topics in complex numbers.

\begin{subject} Math 9.1: Trigonometry
	\hfill
	(3hrs/week)
\end{subject}
This course is offered to all grade 9 students of the Integrated Developmental School. It includes topics in angle unit conversions, trigonometric functions, trigonometric identities, trigonometric equations and solutions of right and oblique triangles.

\begin{subject} Math 10: Pre-Calculus
	\hfill
	(3hrs/week)
\end{subject}
This course covers the advanced concepts in algebra like rational, exponential, logarithmic and other special types of functions. The course also covers special topics including methods of proof, mathematical induction and analytic geometry, and their applications. 

\begin{subject} Math 10.1: Introduction to Statistics
	\hfill
	(3hrs/week)
\end{subject}
This is a one-unit credit course which covers basic concepts in statistics such as the nature of probability and statistics, frequency distributions and their graphs, techniques for data description, probability and counting rules, hypothesis testing, testing means. The course prepares and helps students in performing statistical computations and interpreting results in researches. The course uses and provides experiences for the students to use statistical software such as Excel-Data Analysis and Excel-Megastat in the computations.

\begin{subject} Stat100C: Statistics and Probability
	\hfill
	(4hrs/week)
\end{subject}
This course introduces students to the fundamental concepts of statistics and probability. Students will learn how to analyze data, make informed decisions, and understand the principles of probability. The course emphasizes practical applications in real-life scenarios.

\begin{subject} Math 100C Calculus I
	\hfill
	(4hrs/week)
\end{subject}
This course is offered to Grade 11 students at the Integrated Developmental School, MSU-IIT. The course includes topics on concepts of functions, modeling functions, graphing rational, logarithmic and exponential functions, solving rational, logarithmic and exponential equations and inequalities. The course also includes business math topics such as simple interest, compound interest, annuities, basic concepts of stocks and bonds, and logic

\begin{subject} Math 120C: Calculus II
	\hfill
	(4hrs/week)
\end{subject}
This comprehensive Pre-Calculus course is designed to equip Grade 11 STEM students with the mathematical foundation necessary for success in higher-level calculus and related disciplines. The course encompasses four main components: Analytic Geometry focusing on Conic Sections, Sequences and Series, Circular Functions, and Trigonometry.