\section{Policies for Honors}
To encourage students to aim for excellence, recognition is given to those who performed well in academic and non-academic endeavors in and out of the campus. These students are recognized at the end of each of the first three quarters and at the end of the school year.

\begin{enumerate}[label=(\Alph*)]
	\item \textbf{JUNIOR HIGH SCHOOL}
	
	\begin{enumerate}[label=\Alph{enumi}.\arabic*]
		\item \textbf{Quarterly Awards} \\
		During the Quarter Recognition Awards, the following Awards are given:
		
		\textbf{Academic Honors} are awarded to students who excelled in their studies for the given quarter. To qualify for the Honors Roll, a student must have no grade below 80\% in any subject (including the MAPEH components) and no grade below 85\% in any character grade for the given quarter. Furthermore,he must have not committed any Category C offenses for the quarter.
		\begin{itemize}
			\item The \textbf{First Honors Award} is given to students whose grade point average for the quarter is 94\% or better.
			\item The \textbf{Second Honors Award} is given to students whose grade point average for the quarter is from 92\% to 93.99\%.
			\item The \textbf{Third Honors Award} is given to students whose grade point
			average for the quarter is from 90\% to 91.99\%.
		\end{itemize}
		
		\textbf{Co-Curricular} and \textbf{ Extra-Curricular Awards} are given to students who won in off-campus competitions officially recognized by the school during the quarter.
		
		\textbf{These Awards are given during the 1st, 2nd, and 3rd quarters.}
		
		\item \textbf{Academic Year-End Awards}
		
		At the end of the school year, the same Academic Honors are awarded to the students during the year-end recognition activities. To qualify for the year-end honors roll, a student must have no final grade below 80\% in any subject and in any character grade. Moreover, the student must have no grade below 80\% in any subject and no grade below 85\% in any character grade during the previous quarters. Also, he must have not committed any Category C offenses for the school year.
		
		\textbf{Academic Excellence Awards} \\
		The Academic Excellence Award is given to students who earned the highest academic grade in a particular subject. For the Science and Math where two or more subjects are offered in a year level, the weighted average of the final grades will be used as the basis for the selection of the awardee. 
		
		\textbf{Service Awards} \\
		The Service Award is given to students from any grade level who have rendered exemplary service to the school for the current school year. This particular service must be outside of the expectations of any office held. This award is given upon the recommendation of any faculty member, and need not be awarded every year.
		
		\item \textbf{Completion Awards}
		
		\begin{enumerate}[label=\arabic*.]
			\item The following honors are given during the completion ceremonies
			\begin{center}
				\begin{tabular}{@{}l@{}}
					\textbf{With Highest Honors} \\
					\textbf{High High Honors}\\
					\textbf{With Honors}\\
					\textbf{With Distinction}
				\end{tabular}
			\end{center}
			
			The aforementioned awards will be given to any member of the graduating class who
			\begin{enumerate}[noitemsep]
				\item[a.] does not have any failing grade in any subject in any grading period
				(Grade 7-10) 
				\item[b.] does not have any grade below 80 in their 9th and 10th grades. 
				\item[c.] has completed the last two years of junior high school in IDS 
				\item[d.] has completed the junior high school academic program for four
				consecutive years. 
				\item[e.] has not committed any of the category C offenses for the school year.
				\item[f.] will be ranked according to their overall weighted average (OWA). \\
				
				The OWA will be computed using the formula shown below:
				
				\begin{equation}
					OWA = \frac{\text{\textit{WA Grade 9}} + \text{\textit{WA of 3 grading periods in Grade 10}}}{2}
				\end{equation}
			\end{enumerate}
			
			Where: 
			\begin{align*}
				OWA &= \text{\textit{Overall Weighted Average}} \\
				WA &= \text{\textit{Weighted Average}}
			\end{align*}
			
			\item The following criteria and the corresponding relative weights shall be used in determining the With Highest Honors, With High Honors, With Honors and With Distinction awards.
			
			\vspace{-0.5cm}
			
			\textbf{
			\begin{enumerate}[noitemsep]
					\item[a.] \begin{tabular}[t]{@{}l@{\hspace{11.5em}}l@{}}
						Academic Excellence & $70\%$ \\
					\end{tabular}
					\item[b.] \begin{tabular}[t]{@{}l@{\hspace{2em}}l@{}}
						Co-Curricular/Extra Curricular Excellence & $30\%$ \\
					\end{tabular}
			\end{enumerate}}
			
			The computed values for the OWA are considered as the candidates’Academic Excellence points while the Co-Curricular and Extra Curricular Excellence points are based on their involvement in non-academic pursuits. Hence, completion candidates are expected to submit supporting documents for their community involvement and active participation in authorized student organizations or clubs, literary-musical and athletic activities in the class, year levels, school as well as participation in citywide, regional, inter-regional, national and international contests as approved by the school.
			\item  The following \textbf{Special Awards} are given to qualified students during the Completion Ceremonies: 
			\begin{itemize}
				\item  \textbf{Academic Achievement Award} – This award is given to any of the top 15 candidates who obtained the highest Overall Weighted Average from Grade 7 to Grade 10. 
				\item \textbf{Outstanding Performance in Co-Curricular Activities} – This award is given to any of the top 15 candidates who obtained the highest Co-curricular/Extra Curricular points from Grade 7 to Grade 10.
				\item \textbf{Leadership Award} – This award is given to any JHS officer of the Supreme Student Council who has shown exemplary service to the entire studentry.
				\item  \textbf{Campus Journalism Award (English)} – This award is given to any JHS member of the official English School Paper, The Agong, who has manifested remarkable performance in related competitions held in/off campus. However, the award will not be given if no school paper has been produced during the school year.
				\item \textbf{ Campus Journalism Award (Filipino)} – This award is given to any JHS member of the official Filipino School Paper, Ang Agong, who has manifested remarkable performance in related competitions held in/off campus. However, the award willnot be given if no school paper has been produced during the school year.
				\item  \textbf{Best in Performing Arts (Music)} – This award is given to any JHS member of any Music-related Clubs of IDS who has shown exemplary performance in school programs/activities and has participated in music/song competitions held in/off campus that are officially recognized by the school.
				\item  \textbf{Best in Performing Arts (Dance)} – This award is given to any JHS Dance Club member who has shown exemplary performance in school programs/activities and has participated in dance competitions held in/off campus that are officially recognized by the school.
				\item  \textbf{Athlete of the Year} – This award is given to any JHS student who has done outstanding and remarkable performance in any competition outside IDS that are officially recognized by the school.
			\end{itemize}
		\end{enumerate}
	\end{enumerate}
	
	\item  \textbf{SENIOR HIGH SCHOOL}
	\begin{enumerate}[label=\Alph{enumi}.\arabic*]
		\item  Semestral Awards \\
		\noindent During the Semestral Recognition Awards, the following Awards are given:
		
		\textbf{Academic Honors} are awarded to students who excelled in their studies for the given semester. To qualify for the Honors Roll, a student must have no grade below 85\% in any subject and no grade below 85\% in any character grade for each quarter. Furthermore, he must have not committed any Category C offenses for the school year.
		\begin{itemize}
			\item  The \textbf{First Honors Award} is given to students whose grade point average for the semester is 93\% or better.
			\item  The \textbf{Second Honors Award} is given to students whose grade point average for the semester is from 90\% to 92.99\%.
			\item  The \textbf{Third Honors Award} is given to students whose grade point average for the semester is from 87\% to 89.99\%.
		\end{itemize}
		
		\textbf{Co-Curricular/Extra-Curricular Awards} are given to students who won in off campus competitions that are officially recognized by the school for the given semester. 
		
		\item \textbf{Academic Year – End Awards} \\
		At the end of the school year, the same Academic Honors are awarded to the students during the year-end recognition activities. That is, to qualify for the year-end honors roll, a student must have no grade below 85\% in any subject and no grade below 85\% in any character grade in any quarter.Furthermore, he must not have committed any Category C offenses for the school year. The Overall Weighted Average for the year is the Weighted Average of all the subjects for the two semesters.
		
		\textbf{Strand Academic Excellence Award} \\
		The Strand Academic Excellence Award is given to any honor student who has earned the highest Overall Weighted Average for each strand. Moreover,the student must have no grade below 90\% in any specialized subjects
		
		\textbf{Service Awards} \\
		The Service Award is given to students from any grade level who have rendered exemplary service to the school for the current school year. This particular service must be outside of the expectations of any office held. This award is given upon the recommendation by any faculty member, and this need not be awarded every year. 
		
		\item \textbf{Graduation awards} \\
		\begin{center}
			Batch: \qquad \qquad \textbf{Class Valedictorian} \\
			\qquad \qquad \qquad \quad \textbf{Class Salutatorian} \\
			Per Strand: \qquad \qquad \textbf{With Highest Honors} \\
			\qquad \qquad \qquad \quad \quad \textbf{With High Honors} \\
			\qquad \qquad \qquad  \textbf{3 With Honors}
		\end{center}
		
		\item  The aforementioned awards will be given to any member of the graduating class
		who
		\begin{itemize}
			\item  does not have any grade below 85\% in their 11th and 12th grades;
			\item  has completed the last two years of senior high school in IDS;
			\item  has completed the senior high school academic program for two
			consecutive years; 
			\item  has not committed any of the Category C offenses for the school year; and
			\item  will be ranked based on their Overall Weighted Average from Grade 11 to
			12
		\end{itemize}
		\item The following \textbf{Special Awards} are given during the Graduation Ceremonies:
		
		\textbf{Academic Achievement Award} – This award is given to the Class Valedictorian.
		
		\textbf{Outstanding Performance in Co-Curricular Activities} – This award is given to any member of the graduating class who obtained the highest Co-curricular/Extra Curricular points from Grade 11 to Grade 12.
		
		\textbf{Leadership Award} – This award is given to any SHS officer of the Supreme Student Council who has shown exemplary service to the entire studentry.
		
		\textbf{Campus Journalism Award (English)} – This award is given to any SHS member of the official English School Paper, The Agong, who has manifested remarkable performance in related competitions held in/off campus. However,the award will not be given if no school paper has been produced during the school year.
		
		\textbf{Campus Journalism Award (Filipino)} – This award is given to any SHS memberof the official Filipino School Paper, Ang Agong, who has manifested remarkable performance in related competitions held in/off campus. However,the award will not be given if no school paper has been produced during the school year.
		
		\textbf{Best in Performing Arts (Music)} – This award is given to any SHS member of any Music-related Clubs of IDS who has shown exemplary performance in school programs/activities and has participated in music/song competitions held in/off campus that are officially recognized by the school.
		
		\textbf{Best in Performing Arts (Dance)} – This award is given to any SHS Dance Club member who has shown exemplary performance in school programs/activities and has participated in dance competitions held in/off campus that are officially recognized by the school.
		
		\textbf{Athlete of the Year} – This award is given to any SHS student who has done outstanding and remarkable performance in any competition outside IDS that are officially recognized by the school.
		
		\textbf{Quizzer of the Year} – This award is given to any SHS student who has represented the school and won in off-campus quiz shows that are officially recognized by the school.
		
		\textbf{Debater of the Year} – This award is given to any SHS student who possesses the qualities of an effective public speaker and has represented the school in off campus debate competitions that are officially recognized by the school.
		
	
		
		
		
		
		
		
		
		
		
	\end{enumerate}
	
	
	
	
\end{enumerate}